User-level Grid Monitoring with Inca 2

### 2007-02-24 pubs/papers/hpdc-gmw-2007/paper.tex
tg deployment and text
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6551 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

\item Provides facilities to ease the process of writing test or benchmarks,
deploying them into Inca 2 installations, and sharing them with other Inca 2
users.

\item Periodic tests executed by the monitoring system should be automated and
run from a standard user account.  A user GSI credential should be issued and
used by the monitoring system to test services that require authentication.  
%myproxy stuff
\item Tests should be executed locally on all Grid resources when appropriate so
that all Grid access points available to users are tested.  
\item The configuration of tests should be managed centrally in order to ensure
consistent testing of the resources, rather than by system administrators who
may not use the same information that is available to users.
\item The testing system should easily adapt to new resources and testing
requirements.  In our experience, testing has an iterative refinement process
because Grids are dynamic and the software environment changes over time as
packages are upgraded.  Furthermore, it is often difficult to write and deploy
a test perfectly the first time because of portability issues and incomplete
user documentation.   
\item System administrators should not need to know the details of the
monitoring system in order to troubleshoot problems.  When a problem is
detected the monitoring system should provide system administrators with
sufficient information to locate the problem easily and test repairs.
\item A history of test results (especially any error messages) should be
retained in order to understand the behavior of their Grid over time. This
history should be available through a flexible querying interface.
\item A running monitoring system should have a limited impact on the resources
it measures and should be secure.
\end{enumerate}

@@

\lstset{
  basicstyle=\scriptsize\ttfamily, 
  frame=single,
  keywordstyle=\textbf, 
  identifierstyle=, 
  commentstyle=\scriptsize\ttfamily, 
  stringstyle=\ttfamily, 
  numbers=left, 
  numberstyle=\scriptsize,
  stepnumber=2,
  firstnumber=1,
  showstringspaces=false} 
\begin{figure}
\lstset{language=Perl} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing}}
\lstset{language=XML,keywordstyle={}} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing.out}}
\caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
availability of a Globus GRAM server and (b) its sample output.}
\end{figure}

@@

TeraGrid's Inca 2 agent, depot and consumer components are hosted at SDSC on 
sapa.sdsc.edu, a XX machine.  A reporter repository for TeraGrid is also hosted
at SDSC on login-linux.sdsc.edu, a XX machine.  TeraGrid's 20 compute resources
each run a reporter manager and regularly execute an average of 109 reporters
to perform 48 cross-site, 20 grid, 28 cluster, 9 data, 2 user tool, and 2
security tests.

@@

TeraGrid currently has six status pages: a summary of software stack test
failures, a detailed grid of software test results, a page showing grid job
usage, results for security tests, results for secure mds tests, and a list of
all running reporters.

\begin{figure}[hbt]
  \centering
  \includegraphics[scale=0.5]{status-page.eps}
  \caption{TeraGrid CTSS status page.}
  \label{status_page_fig}
\end{figure}

>>>>

\item Provides facilities to ease the process of writing tests or benchmarks
and deploying them into Inca 2 installations. (improved)

\item Provides facilities for sharing tests or benchmarks with other Inca 2
users in order to promote sharing of each other's expertise (new)

\item Easily adapts to new resources and monitoring requirements in order to
facilitate maintenance of a running Inca 2 deployment. (improved)

\item Stores and archives monitoring results (especially any error messages) 
in order to understand the behavior of a Grid over time. The results
are available through a flexible querying interface. (improved)

%myproxy stuff
\item A running monitoring system should have a limited impact on the resources
it measures and should be secure.
\end{enumerate}

@@

\lstset{
  basicstyle=\scriptsize\ttfamily, 
  frame=single,
  keywordstyle=\textbf, 
  identifierstyle=, 
  commentstyle=\scriptsize\ttfamily, 
  stringstyle=\ttfamily, 
  numbers=left, 
  numberstyle=\scriptsize,
  stepnumber=2,
  firstnumber=1,
  showstringspaces=false} 
\begin{figure}
\lstset{language=Perl} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing}}
\lstset{language=XML,keywordstyle={}} 
\subfigure[]{\lstinputlisting{grid.globus.gramPing.out}}
\caption{\label{pingReporter}(a) An Inca reporter that tests the user-level
availability of a Globus GRAM server and (b) an output sample.}
\end{figure}

@@

TeraGrid's Inca 2 agent, depot and consumer components are hosted at SDSC on 
sapa.sdsc.edu.  A reporter repository for TeraGrid is also hosted
at SDSC on login-linux.sdsc.edu.  TeraGrid's 19 compute resources
each run a reporter manager and regularly execute an average of 109 reporters
to perform 48 cross-site, 20 grid, 28 cluster, 9 data, 2 user tool, and 2
security tests.  Figure~\ref{tg_deploy_fig} illustrates TeraGrid's Inca 2 
deployment configuration.

\begin{figure}[hbt]
  \centering
  \includegraphics[scale=0.6]{tg-deploy.eps}
  \caption{TeraGrid's Inca 2 Deployment.}
  \label{tg_deploy_fig}
\end{figure}

@@

TeraGrid currently has six status pages: a summary of CTSS test
failures, a detailed grid of CTSS test results, a page showing grid job
usage, results for security tests, results for secure mds tests, and a list of
all running reporters.

Figure~\ref{status_page_fig} shows a portion of the TeraGrid detailed CTSS test result
page.  CTSS software packages are listed along the column and TeraGrid
resources (anonymized) in the header rows.  Test results for each package and
resource are shown in the table body rows.

\begin{figure}[hbt]
  \centering
  \includegraphics[scale=0.4]{status-page.eps}
  \caption{TeraGrid CTSS status page.}
  \label{status_page_fig}
\end{figure}
